Data Preparation

### 2019-01-09 Data Preparation.Rmd
Importing dataset for courses

---
title: "Data Preparation"
author: "DARS"
date: "`r Sys.Date()`"
output: pdf_document
---
# Libraries:
```{r setup, include=FALSE}
library(tidyverse)
library(tidytext)

@@

>>>>

---
title: "Data Preparation"
author: "DARS"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, message = FALSE}
library(tidyverse)
library(tidytext)

@@

## Course Data
We import three spreadsheets from the drive and transform them into the so-called *tidy format*. The tibble `d_course` contains information at the course-level such as in which cluster and concentration(s) they belong and in which period(s) they are offered, the tibble `d_assessment` indicates which type(s) of assessment each course contains with one row per course-assessment and the tibble `d_ILO` indicates which AoD(s) the intended learning objectives (ILOs) of the courses cover with one row per course-ILO-AoD.

```{r import data from drive}
d_course <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1655700848') %>%
  mutate(`Missing from ILO File` = as.logical(`Missing from ILO File`))
print(d_course)

d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
  select(- `Comment on Assessment`) %>%
  gather(Assessment, assessment_covered, - Code, factor_key = T) %>%
  mutate(assessment_covered = as.logical(assessment_covered)) %>%
  filter(assessment_covered) %>%
  select(- assessment_covered) %>%
  arrange(Code)
print(d_assessment)

d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050') %>%
  select(- c(Comments, Comments_for_Jeroen)) %>%
  gather(AoD, AoD_covered, -c(Code, Objectives), factor_key = T) %>%
  mutate(AoD_covered = as.logical(AoD_covered)) %>%
  rename(ILO = Objectives) %>%
  filter(AoD_covered) %>%
  select(- AoD_covered) %>%
  arrange(Code)
print(d_ILO)
```
